Extracting Function Signature from R Program Traces

### 2020-05-13 paper/main.tex
final type grammar

%
%
\subsubsection{Structs}

@@

We did not discuss ${\bf expression}$, ${\bf language}$, ${\bf symbol}$, ${\bf externalptr}$, ${\bf pairlist}$, ${\bf S4}$, and ${\bf weakref}$ types throughout this section.
They occur \AT{rarely}, and are by-and-large uninteresting to most R programmers.
\AT{Fill in...}

>>>>

%
%
\subsubsection{Structs}
\label{subsec:structs}

@@

We have discussed most of these types throughout this section, with some notable exceptions.
${\bf expression}$, ${\bf language}$, ${\bf symbol}$, ${\bf externalptr}$, ${\bf pairlist}$, ${\bf S4}$, and ${\bf weakref}$ types occur \AT{rarely}, and are by-and-large uninteresting to most R programmers.
\AT{Fill in details of these basic types.}
% $S$ and $V$ are scalar and vector primitives, with vectors taking the form $S[]$.
% The scalar type $S$ can be either a base type $B$ (one of the 6 primitives in R), or an NA-able base type (roughly, $\string^B$).
One other type we did not discuss is the union type $T_1 \, | \, T_2$, which is supported by \contractr and generated by \typetracer when it cannot find some way to consolidate argument types (for example, if an argument is observed to be ${\bf chr}$ and ${\bf int}$, \typetracer will ascribe type ${\bf chr} \, | \, {\bf int}$ to it).
And while not generated by \typetracer (recall discussion in Section~\ref{subsec:structs}), user-defined struct types have the form ${\bf struct}\langle F_1, ..., F_n \rangle$, with fields $F_i$ being name $:$ type pairs.
